Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-27 manuscript.Rmd
Methods Revisions

After the target list of social work journal titles was finalized, we attempted
to identify all article records from these journals using three major databases
on the EbscoHost platform (PscyINFO, Social Science Abstracts, and Social Work
Abstracts) and 46 minor databases on Proquest (e.g., ERIC, Sociological
Abstracts, Worldwide Political Science Abstracts).  Using the ``publication
source`` fields of the search interface, we searched for article records that
contained the names of each social work journal.  Searches were limited to a
quarter century time-frame, 1989 to 2013.  We excluded years 2014 and 2015 due
to delays in indexing of records that were observed.  In the extraction
process, we also limited the records to only those classified as "journal
articles," thereby excluding other types of scholarly communications, such as
editorials, comments on articles, letters to the editor, book reviews, and
obituaries.

@@

In addition to post-processing original article records, R was also used for
all other data analysis.  R was an ideal analytic tool because it is
open-source and has a suite of related tools for producing reproducible
research.  More specifically, all the source code is written using Rmarkdown --
an open-source system that integrates data management, data analysis, and the
written report.  The source code and data extracts is also curated at openICPSR
of the Inter-university Consotrium for Political and Social Research of the
University of Michigan.  The source code is also available from the first
author's GitHub repository, where the code will be maintained and updated to
support future research projects. It should be noted that the full data files
cannot be made publicly available because these are considered proprietary data
of the database services.  However, to ensure full compliance with the best
practices of reproducible research (cite King), we have [BRYAN -- DESCRIBE HERE
HOW THE PS JOURNAL HANDLES THIS ISSUE ... ASSUME THE EDITOR IS ON-BOARD WITH
THIS APPROACH].

>>>>

After the target list of social work journal titles was finalized, we attempted
to identify all article records from these journals using three major databases
on the EbscoHost platform (PsycINFO, Social Science Abstracts, and Social Work
Abstracts) and 46 minor databases on ProQuest (e.g., ERIC, Sociological
Abstracts, Worldwide Political Science Abstracts).  Using the ``publication
source`` fields of the search interface, we searched for article records that
contained the names of each social work journal.  Searches were limited to a
quarter century time-frame, 1989 to 2013.  We excluded years 2014 and 2015 due
to delays in indexing of records that were observed.  In the extraction
process, we also limited the records to only those classified as "journal
articles," thereby excluding other types of scholarly communications, such as
editorials, comments on articles, letters to the editor, book reviews, and
obituaries.

@@

In addition to post-processing original article records, R was also used for
all other data analysis.  R was an ideal analytic tool because it is
open-source and has a suite of related tools for producing reproducible
research.  More specifically, all the source code is written using Rmarkdown --
an open-source system that integrates data management, data analysis, and the
written report.  The source code and data extracts are also curated at openICPSR
of the Inter-university Consotrium for Political and Social Research of the
University of Michigan.  The source code is also available from the first
author's GitHub repository, where the code will be maintained and updated to
support future research projects. It should be noted that the full data files
cannot be made publicly available because these are considered proprietary data
of the database services.  However, to ensure full compliance with the best
practices of reproducible research (cite King), we have provided the journal editor with the following conditions under which we would release the data: (1) the requester must be affilitated with an insitution that provides access to both the EbscoHost and ProQuest platforms along with the databases used in this study or (2) hold a personal subscription to each platform and the databases utilized here.  This is designed to meet the standards of maximum allowable data transparency while respecting the proprietary nature of the data.
